\section{Global Functions}
This section describes the important global functions that we have created and used in the verification of the system.

\subsection{parentConstraintViolated}
This function checks if the parent constraint is violated. 
The parent constraint is that the father cannot be alone with the girls, and that the mother cannot be alone with the boys.
It takes a group of people and a person type for a parent and a child.
If the constraint is violated the function returns true, if not it returns false.

\subsection{thiefConstraintViolated}
As the above function this one returns true if the constraint is violated and false if it is not.
The constraint states that the thief cannot be alone with the family.
This constraint can be specified as that there may not be anyone with the thief if there is not a police officer with the thief.

\subsection{verifyGroup}
VerifyGroups checks if a group of people adheres to the constraints defined in the two above functions, namely the parent constraint for both the mother and the father and the thief constraint.
If any of these constraints are violated the function returns false.
If none of the constraints are violated the function returns true.

\subsection{verify}
Verify uses the function verifyGroup on three groups of people; the group of people on the left and right sides of the river as well as the group of people on the boat.
If all these groups are verified, the function returns true -- otherwise it returns false.