\chapter{Implementation}
\label{chap:implementation}
\myTop{In this chapter we describe how we implement the concepts described in \chapref{chap:design}.
This chapter is divided into three sections where the three main components of our system are described, namely \nameref{sec:pglib},  \nameref{sec:projGroupRoomImpl}, and \nameref{sec:manProjGrpImpl}.
The implementation details presented here are paramount for \chapref{chap:test} and \chapref{chap:evalProduct}.}
From \secref{sec:architecture} we know that there are three components, which must be implemented by us -- the administration tool to manage project group, the project group, and the virtual group room. 
The administration tool is implemented as an admin tool, which, as described in \secref{par:admintool}, is a special Moodle plugin type. 

%Recall \secref{sub:interActivities} where we designed the concept of project groups.
In the implementation of the project group concept we are faced with two choices. 
It can be implemented as courses (see \secref{sub:courses}) by creating a new view for the course page. 
By doing so we solve the problem of both implementing project groups and the virtual group room.
This will make it possible to use activity modules, described in \secref{par:activitymodules}, in the virtual group room.
Another option is to make a local plugin, which, as described in \secref{par:localplugin}, gives us basic functionality such as database installation and the possibility to extend the built-in navigation block. 
With a local plugin we cannot use activity modules since they are too strongly connected to courses. 
Instead we can use \block{}s for the functionality. 
%We choose to implement the \detdeandrelaver{}s as blocks as described in \secref{sub:interActivities}.
We choose to make a local plugin.

The local plugin includes both the project group library and the virtual group room.


\section{Project Group Library}
\label{sec:pglib}
%The \viewroom[] is implemented in the file \moodlefile{/local/projectgroup/view.php} and  t
The project group library is implemented in the file \moodlefile{/local/projectgroup/lib.php}. 
The library includes several other files. % such as various helper files and one for each of the other three peer-groups. 
One for each of our peer-groups and several helper files. 
Our contribution to the library is located in the library file itself. 
%The project group library is build up by several files and consist of several functions and classes.
%The library itself is created by our subgroup, but it includes a file from each of the other groups. 
%This following sections only explains the functionality implemented by our subgroup. 
The library consists of approximately $300$ lines of code, including comments and whitespace and excluding any included files. 
All the functionality in the library is auxiliary functionality for the entire system. 
%In the later sections we refer to several functions, which are all located in the library. 

The following sections explain how project groups are put into a \moodle{} context and how we ensure that users have the correct permissions.

\input{input/implementation/overwriteContext.tex}
\FloatBarrier
\input{input/implementation/ensuringpermissions}

\FloatBarrier

\input{input/implementation/projectGroupRoom.tex}

\input{input/implementation/manageProjectGroups.tex}







