%\chapter{Demo Meeting}

\section{Lea Gustavson Demo Meeting Sprint 4}
\label{app:leademo}
The documentation of this interview is written by the \timelinegroup{} group. \\ \ \\
Date: 07/05/12
Participants: Lea Gustavson, Anders Eiler, Kim Jakobsen, Henrik Koch, Jesper Dalgas \\
Interviewer: Anders Eiler

Lea is given a complete walk-through of our system.
A casual conversation is conducted about the different elements.
The following is a summary of the conversation between Lea and Eiler:

\subsection*{Meetings}
\begin{itemize}
	\item A pop-up appears when creation of a meeting is complete, it is disruptive.
	\item When a user enters the page for a meeting, no back button is visible.
\end{itemize}


\subsection*{Timeline}
\begin{itemize}
	\item It would be nice if it was possible to show scheduled lectures on the timeline.
\end{itemize}


\subsection*{Tasks}
\begin{itemize}
	\item When creating a task, the calender does not close when a date is selected.
\end{itemize}


\subsection*{Wall}
\begin{itemize}
	\item If several comments exist on an item, it can disrupt the clarity of the wall. It could be nice if older comments collapsed and only new comments are displayed in full.
	\item The current filter options were not useful, Lea suggest more filtering options.
	\item It is not all comments that are relevant for the supervisor, and some comments are for the group only. An option to send the message to the supervisor would resolve this problem.
	\item The structure is very clear and gives a good overview.
\end{itemize}


\subsection*{Blackboard}
\begin{itemize}
	\item It is currently not possible to assign a name to a blackboard.
\end{itemize}


\subsection*{Other}
\begin{itemize}
	\item The overall layout seems simple and easy to use.
	\item The meeting feature is very attractive and Leas thinks that her group will use it often.
	\item They use SVN for writing the report, it could be intergrated with moodle in some way.
	\item Lea explains that group rooms should be private for the group.
\end{itemize}

\begin{comment}
\subsection*{Comments from the observers}
\begin{itemize}
	\item Meetings: It would be nice if it was possible to see what other activities that is arranged on a given date. This is relevant when creating a new meeting.(Henrik Koch)
	\item General: The name of the buttons are not consistent, some are labeled `` submit'' and others ``save''. (Kim Ahlstrøm)
	\item If the wall only contains a few elements, it displays the next page button even though only one page is available. (Kim Ahlstrøm)
	\item Lea was not able to edit group settings because she was not admin. It is a problem that admin rights are required to edit a group. (Kim Ahlstrøm)
	\item It would be nice with a small calender view in one of the sitebars (Anders Eiler)
\end{itemize}
\end{comment}


\section{Mathilde Gammelgaard Demo Meeting Sprint 4}
\label{app:mathildedemo}
The documentation of this interview is written by the \timelinegroup{} group. \\ \ \\
Date: 09-05-12
Participants: Mathilde Gammelgaard , Anders Eiler, Kim Jakobsen \\
Interviewer: Anders Eiler

Mathilde is given a complete walkthrough of our system.
A casual conversation is conducted about the different elements.
The following is a summary of the conversation between Mathilde and Eiler:

\subsection*{General}
\begin{itemize}
	\item Not very user friendly.
\end{itemize}


\subsection*{Members}
\begin{itemize}
	\item Considering that the group members know each other, it takes up a lot of space.
\end{itemize}


\subsection*{Meetings}
\begin{itemize}
	\item Data is not danish standard.
	\item Standard meeting should not include supervisor.
\end{itemize}


\subsection*{Timeline}
\begin{itemize}
	\item It is a good thing that it is dynamic.
	\item Four months makes the horizontal timeline chaotic.
	\item Good for overview.
\end{itemize}


\subsection*{Tasks}
\begin{itemize}
	\item When entering the name of the title one must first delete the ``Task title'' text.
	\item A color should be uniquely attached to a type.
	\item If a huge amount of tasks exit, a view with tasks of the day is wanted.
	\item A task should contain subtasks.
	\item In task overview there need to be added a ``assigned to'' column.
\end{itemize}


\subsection*{Wall}
\begin{itemize}
	\item It is important that the supervisor is not able to see all messages and files
	\item It should be an active task to post something to the supervisor
	\item There is to much emphasizes on filters and item information on the wall. It is disturbing.
	\item It is a good thing that it is similar to Facebook, it makes it easy to learn.
	\item Less spaceing between text
	\item When handling multiple documents, an explorer like appearance would be appreciated.
\end{itemize}


\subsection*{Blackbaard}
NOTE: Did not work, but we talked about it.

\begin{itemize}
	\item Not very usable.
	\item Add arrow functionality.
	\item Add equation options.
\end{itemize}

\begin{comment}
\subsection*{Comments from the observers}
\begin{itemize}
	\item Task: It is possible to assign task to the supervisor, seems odd. --Kjakob09 09:19, 9 May 2012 (UTC)
	\item Task: Assign task to members form is not consistent with the rest of the system. (Eiler)
	\item Task: Overdue tasks should be marked with an ! (Eiler)
\end{itemize}
\end{comment}

