\section{Lene Winther Even Demo Meeting Sprint 4}
\label{sec:lenedemotwo}
Group members present: Alex Bondo Andersen, Kim Ahlstr\o{}m Jakobsen, Mikael Midtgaard, and Rasmus Veiergang Prentow\\
Administrative personnel present: Lene Winther Even and Camilla G\ae{}raa Larsen\\

This demo meeting was conducted on May 9\ths{} in the group room at Cassiopeia at Aalborg University.
Along with Lene was her office trainee Camilla G\ae{}raa Larsen. 
Lene used the system and gave feedback, while Camilla observed and gave her thoughts on the system.

The following is the relevant parts of the demo meeting.

\subsection*{Using The System}
On the page to add a new project group Lene used the filter function to search for users to add to the group.
She successfully found and added the first user.
When attempting to add an additional user to the group she added another filter. 
This resulted in no users matching both filter. 
However, she quickly discovered the mistake and removed the first filter, which showed the user she was looking for.

When using the list of the project groups Lene expected to be redirected to the group page when pressing on a group link.
Instead she was redirected to a list of group members.
From the list she added another member to a group without any problems.

On a project group page Lene used the functionality developed by the \supervisorgroup group.
She uploaded a file and commented on the problem, and was satisfied with the functionality of it.
She did, however, think that the user interface needed to be improved.

\subsection*{Additional Comments}

\begin{itemize}
	\item It would be preferred to have central database that contained information on all the groups of Aalborg University.
Additionally, people should be able to create groups for different purposes.
  \item The fullname attribute is not used in practice.
	\item There are a number of problems with having several different Moodle systems at Aalborg University insted of having just one.
	\item Camilla thinks that overall the system we developed seems to be working well.
	\item There should be a way to remove the old filters in the same action as adding a new filter.
	\item The list of project groups should have a column displaying the supervisor.
	\item It should be possible to sort the list by the different columns - both ascending and descending order.
	\item In the future the system could be expanded to show how many hours supervisors use on their groups, so it could be used for hour calcutions, which is a task that the administrative personnel at Aalborg University do.
\end{itemize}