\section{Lene Winther Even Demo Meeting Sprint 3}
\label{sec:lenedemoone}
Group members present: Alex Bondo Andersen, Kim Ahlstr\o{}m Jakobsen, and Mikael Midtgaard\\
Administrative personnel present: Lene Winther Even\\

This demo meeting was conducted on April 4\ths{} our the group room at Cassiopeia at Aalborg University.
We briefly showed Lene the administrative tool that we implemented and asked her to use it and give feedback.

The following is the relevant parts of the demo meeting.

\subsection*{Using the System}
Lene tried to add a project group with a few members.
She noted that the list of members added and the list of users not added was reversed compared to the creation of courses in the \moodle{} template she was used to.
She also mentioned that the search field for users in the system is usually located under the two lists of users, not above.
She had trouble with the the filtering functionality because a new filter did not replace an old one, but added it in conjunction with the existing one(s).

After the project group was created she was asked to find the group and alter it.
She could not find the project group because there were simply too many project groups.
She tried to use the internal search field, but it did not help.
She suggested that there should be a search functionality similar to that of members to add to a project group.

\subsection*{Additional Comments}
After Lene tried using the system she had a few comments and ideas, which are presented below.
\begin{itemize}
	\item The list of members does not contain the full name of the users.
	It would greatly help to have the full name to identify the students and supervisors.
	\item When asked if she could see any use of a recursive tree structure, she could not come up with any work task where she would benefit from it.
	\item The member overview seems useful to identify users.
	\item Perhaps instead of using the term ``Full Name'', the term ``Project Group Name'' would be better.
	\item To avoid double work an integration with ADMDB would be great.
	ADMDB is the system where project groups are inserted at semester start.
	\begin{itemize}
		\item It should be possible to get every project group of a semester at a time.
		\item Supervisors of project groups should be retrieved from from ADMDB as well.
		\item ADMDB is only used at Institute of Computer Science.
	\end{itemize}
\end{itemize}
