\section{Development Practices} %remember to say how we work with costumers

\subsection{Choosing a Development Method}
%because many people -> agile. our version of scrum
We need a development method that takes the large number of people we are into account.
Furthermore, the development method also needs to take into account that we are working on a platform (namely Moodle), which most of us are unfamiliar with.

We choose to use the development method Scrum(see section \ref{par:scrum}) with a few changes.
The reason why we cannot use Scrum in its original form is that we do not have all the required personnel. 
Scrum requires an on-site costumer and a product owner.
We have neither, so we have to make some modifications to the development method.
Instead we have acquired some customers from which we get requirements and feedback for the system we are developing.
As the \groupname{} we are responsible for creating the administrative part of the system as well as creating the project group page.
Therefore we are in contact with administrative personnel at Aalborg University, which serve as costumers.
The costumers for the functionality of the group page are the three other groups in this multi-project.
How we work together with our costumers will be described later in this section.

\subsection{Utilizing the Development Method}
%utilizing agile methods -> we don't know shit so its good
Since we are not familiar with Moodle, from the beginning of the project we do not have a full understanding of how the entirety of the system should be structured and created.
We solve this problem by dividing the development process into a number of sprints.
Ideally after each sprint we should have a fully functional system, which is in such a state that it can be shipped.
This is not entirely the case, since we need a lot of information before we can start programming.
%sprints
To handle this our first sprint will consist of information gathering; we study the Moodle platform as well as interview our costumers in order to get requirements.
%product backlog
These requirements are used to create feature descriptions, which are used to fill the product backlog.
%sprint backlog
At the beginning of each succeeding sprints in our group we choose items from the product backlog and move them to the sprint backlog, which is a list of features we expect to implement in the particular sprint.
%planning poker
In order to choose which items to move to the sprint backlog we assign each item currently in the product backlog a number of story points.
We do this by playing planning poker, which is a card game where we all give our estimates of the items on the backlog simultaneously, and then discuss the estimates if there is a significant difference between us.
%burndown chart
As we progress in the sprint the number of remaining number story points starts to dwindle. 
We keep track of this by a burn-down chart, which is a physical chart with a line that shows the expected progress.
The total number of remaining story points are plotted into the graph each day, so we can see if we are progressing at a satisfactory rate.

\subsection{The Development Method Across Groups} %change this title if you are so fucking clever that you think you can do better

%daily scrum meetings

%weekly casual scrum og scrum meetings



%sprint planning meetings

%demo meetings



%TDD